MLH1 Results Outline

### 2020-02-04 doc/Main_Report_Results.rmd
debugging and Cleaning up Main Results file

exactRLRT(MLH1var_M1) #strain
as.data.frame( round(summary(MLH1var_M1)$tTable, 6))

@@

as.data.frame( round(summary(M1.cv_co)$tTable, 6))

@@

summary(MLH1var_M3)
anova(MLH1var_M3)  
as.data.frame( round(summary(MLH1var_M3)$tTable, 6))

@@

anova(MLH1cv_M3)
as.data.frame( round(summary(M1.cv_co)$tTable, 6))

@@

summary(MLH1var_M3_Q12)
anova(MLH1var_M3_Q12)  
as.data.frame( round(summary(MLH1var_M3_Q12)$tTable, 6))

@@

drop1(MLH1var_M4, test="Chisq")
anova(MLH1var_M4)
as.data.frame( round(summary(MLH1var_M4)$tTable, 6))

@@

summary(MLH1cv_M4)

drop1(MLH1cv_M4, test="Chisq")
anova(MLH1cv_M4)  
exactRLRT(MLH1cv_M4)
as.data.frame( round(summary(MLH1cv_M4)$tTable, 6))

### Q12 var
MLH1var_M4_Q12 <- lm( var ~ subsp*sex*strain, data=Q12_mouse_table_w.Ages )
anova(MLH1var_M4_Q12)
as.data.frame( round(summary(MLH1var_M4_Q12)$coefficients, 6))

#Q12 cv
MLH1cv_M4_Q12 <- lm( cV ~ subsp*sex*strain, data=Q12_mouse_table_w.Ages )

summary(MLH1cv_M4_Q12)
anova(MLH1cv_M4_Q12)#sex large F

@@

Main figure, MLH1 strain avs on top, chrm proportion bar plot on bottom

@@

@@

@@

## DMC1 Results Spermatocytes

@@

```{r DMC1.setup, echo=FALSE, eval=FALSE}
#load DMC1 csv
DMC1.DF <- read.csv("~./DMC1/newJuviQuant.csv", header = TRUE)

@@

DMC1.mean.obs.Z <- ddply(.data=DMC1.DF[DMC1.DF$stage == "Z",],
                 .(category),
                 summarize, 
                 mean.count = mean( total.count)
)
DMC1.mean.obs.Z$stage <- "Z"

#these tables are merged latter

### Testing Normality Assumptions

```{r normality, echo=FALSE, warning=FALSE, eval=FALSE}
#histograms for each

@@

```{r DMC1.plot, echo=FALSE, warning=FALSE, eval=FALSE}
#think of better color scheme
#make the jitter col thinner or make the stacked dots.
#remember that box-plots add outlier dots.
#change y labels

@@

DMC1.boxplot <- ggplot(aes(x=strain, y=total.count, color=stage), data=DMC1.DF[DMC1.DF$stage != "P",])+
  geom_boxplot(aes(alpha=.5))+geom_jitter()+ggtitle("DMC1 averages in juvenile mice")
  DMC1.boxplot
  #this will add neat bars, but still need to figure out what groups ect it's actually using
#THE stat_compare function adds a arm thing and pvalue for 
#  stat_compare_means(comparisons = my_comparisons)

@@

@@

```{r DMC1.subsampling, echo=FALSE, eval=FALSE}

@@

plot.pvals.L <- ggplot(bunchOpvals.L, aes(bunchOpvals.L) )+geom_histogram(bins = 50)+ ggtitle("1000 rep t-tests sample size 25, High vs Low Leptotene")+geom_vline(xintercept=ttest.HighLow.L$p.value, linetype="dotted", color="red")

plot.pvals.Z <- ggplot(bunchOpvals.Z, aes(bunchOpvals.Z) )+geom_histogram(bins = 50)+ ggtitle("1000 rep t-tests sample size 25, High vs Low Zygotene")+geom_vline(xintercept=ttest.HighLow.Z$p.value, linetype="dotted", color="red")
plot.pvals.L
plot.pvals.Z

@@

```{r DMC1_MLH1.cor, echo=FALSE, eval=FALSE}
#make category averages from AP_mouse_table.HQ
mean.MLH1.obs <- ddply(.data=AP_mouse_table.HQ,
                 .(category),
                 summarize, 
                 mean.MLH1 = mean(mean_co),
                 var.MLH1 = var(mean_co)
)

@@

The correlation with MLH1 and leptotene cells is r MLH1.DMC1.L_cor.

The correlation with MLH1 and zygotene cells is r MLH1.DMC1.Z_cor.

# Single Bivalent Patterns

@@

# Blank

@@

```{r DMC1_t.tests, echo=FALSE, warning=FALSE, eval=FALSE}
#2. t-tests for the DMC1 counts 
#need to account for sample sizes when comparing t.tests (KAZ and G don't have equal across )
#best case scnario -- more microscoping to get ~20 cells for each stage by strain combo

>>>>

exactRLRT(MLH1var_M1) #strain
as.data.frame( round(summary(MLH1var_M1)$coefficients, 6))

@@

as.data.frame( round(summary(MLH1cv_M1)$coefficients, 6))

@@

summary(MLH1var_M3)
anova(MLH1var_M3)  
as.data.frame( round(summary(MLH1var_M3)$coefficients, 6))

@@

anova(MLH1cv_M3)
as.data.frame( round(summary(MLH1cv_M3)$coefficients, 6))

@@

summary(MLH1var_M3_Q12)
anova(MLH1var_M3_Q12)  
as.data.frame( round(summary(MLH1var_M3_Q12)$coefficients, 6))

@@

drop1(MLH1var_M4, test="Chisq")
anova(MLH1var_M4)
as.data.frame( round(summary(MLH1var_M4)$coefficients, 6))

@@

summary(MLH1cv_M4)
anova(MLH1cv_M4)  
as.data.frame( round(summary(MLH1cv_M4)$coefficients, 6))

### Q12 var
MLH1var_M4_Q12 <- lm( var ~ sex*strain, data=Q12_mouse_table_w.Ages )

summary(MLH1var_M4_Q12)

anova(MLH1var_M4_Q12)
as.data.frame( round(summary(MLH1var_M4_Q12)$coefficients, 6))

#Q12 cv
MLH1cv_M4_Q12 <- lm( cV ~ sex*strain, data=Q12_mouse_table_w.Ages )

summary(MLH1cv_M4_Q12)
anova(MLH1cv_M4_Q12)

@@

work more on figure 1. Main figure, MLH1 strain avs on top, chrm proportion bar plot on bottom

@@

What are the steps the each chunks walk through.

@@

#try adding the BivData version of the proportions

@@

# DMC1 Results Spermatocytes

@@

```{r DMC1.setup, echo=FALSE}
#load DMC1 csv
#DMC1.DF <- read.csv("~./DMC1/newJuviQuant.csv", header = TRUE)
DMC1.DF <- read.csv("~./MLH1repo/data/DMC1newJuviQuant.csv", header = TRUE)

@@

DMC1.mean.obs.Z <- ddply(.data=DMC1.DF[DMC1.DF$stage == "Z",],
                 .(category),
                 summarize, 
                 mean.count = mean( total.count)
)
DMC1.mean.obs.Z$stage <- "Z"
```

```{r normality, echo=FALSE, warning=FALSE, eval=FALSE}

#these are histogram plots for testing Normality shape -- move to supplemenatry section

@@

```{r DMC1.plot, echo=FALSE, warning=FALSE}
#think of better color scheme
#make the jitter col thinner or make the stacked dots.
#remember that box-plots add outlier dots.
#change y labels

@@

DMC1.boxplot <- ggplot(aes(x=strain, y=total.count, color=stage), data=DMC1.DF[DMC1.DF$stage != "P",])+
  geom_boxplot(aes(alpha=.5))+geom_jitter()+ggtitle("DMC1 averages in juvenile mice")

DMC1.boxplot
  #this will add neat bars, but still need to figure out what groups ect it's actually using
#THE stat_compare function adds a arm thing and pvalue for 
#  stat_compare_means(comparisons = my_comparisons)

@@

Summary:

The distributions of counts is close to normal (also the higher count is better than the MLH1 counts)

@@

```{r DMC1.subsampling, echo=FALSE}

@@

#plot.pvals.L <- ggplot(bunchOpvals.L, aes(bunchOpvals.L) )+geom_histogram(bins = 50)+ ggtitle("1000 rep t-tests sample size 25, High vs Low Leptotene")+geom_vline(xintercept=ttest.HighLow.L$p.value, linetype="dotted", color="red")

#plot.pvals.Z <- ggplot(bunchOpvals.Z, aes(bunchOpvals.Z) )+geom_histogram(bins = 50)+ ggtitle("1000 rep t-tests sample size 25, High vs Low Zygotene")+geom_vline(xintercept=ttest.HighLow.Z$p.value, linetype="dotted", color="red")
#plot.pvals.L
#plot.pvals.Z

@@

```{r DMC1_MLH1.cor, echo=FALSE}
#make category averages from AP_mouse_table.HQ
mean.MLH1.obs <- ddply(.data=AP_mouse_table.HQ,
                 .(category),
                 summarize, 
                 mean.MLH1 = mean(mean_co),
                 var.MLH1 = var(mean_co)
)

@@

The correlation with MLH1 and leptotene cells is `r MLH1.DMC1.L_cor`.

The correlation with MLH1 and zygotene cells is `r MLH1.DMC1.Z_cor`.

```{r DMC1_t.tests, echo=FALSE, warning=FALSE}
#2. t-tests for the DMC1 counts 
#need to account for sample sizes when comparing t.tests (KAZ and G don't have equal across )
#best case scnario -- more microscoping to get ~20 cells for each stage by strain combo

<!--
 Single Bivalent Patterns

@@

@@
